### 2016-11-17 paper/evaluation.tex
fixed latex error - missing enclosing }
Updated description of maven commands

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include the Linux \emph{sysstat}
package to measure performance, \emph{git} to fetch subjects,
\emph{Java 8} to build and test subjects, and \emph{Python 3.4} to run
our evaluation scripts. For replication, we provide all the source
artifacts publicly available at \Fix{create gh-pages}, including
supporting scripts (\eg, the script that test subjects and generates
the raw data), the full list of projects, and a \emph{Vagrantfile} to
emulate our hardware and all software dependencies properly configured.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.  To avoid inflating
the measured time, we first compile the sources files (see
Figure~\ref{fig:mvn-execution}, line 1) and later (see
Figure~\ref{fig:mvn-execution}, line 2), we ran the tests ignoring
non-related tasks (\eg, \emph{javadoc} generation). In addition, when
we run a subject's test suite, we operate Maven in offline mode to
limit the network access, avoiding any unnecessary package update as
all required \emph{jars} are available locally. We also considered the
execution of all subjects enforcing sequential execution to avoid
having the real time cost masked by the use of any parallel setting
mentioned in Section~\ref{sec:modes}.  After the test execution, we
use a simple regular expression over the builder output to extract the
elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Compiling and testing a Maven
    subject: line 1 compiles all subject's source artifacts and make
    them available in a local repository (\ie, directory \emph{.m2} in
    the user's home directory); line 2 runs the tests in offline mode
    ignoring javadoc generation.}
\end{figure}

@@

Considering the groups \emph{medium} and \emph{long} (\Fix{X} subjects), we
investigated the relationship between the number of tests cases and the time
cost from subjects. \Fix{Explain what is correlation and how it is computed.}
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that the number
of tests cases are not related to the elapsed time.  \Fix{explain briefly what
dominates a test execution/types of tests}.Results indicate that
\Fix{...conclusion...}.

>>>>

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include the Linux \emph{sysstat}
package to measure performance, \emph{git} to fetch subjects,
\emph{Java 8} and \emph{Maven 3} to build and test subjects, and
\emph{Python 3.4} to run our evaluation scripts. For replication, we
provide all the source artifacts publicly available at \Fix{create
gh-pages}, including supporting scripts (\eg, the script that test
subjects and generates the raw data), the full list of projects, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies properly configured.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} illustrates the commands used in our
scripts to test each subject.  To avoid inflating the measured time,
we first compile the sources files (line 1) and later, we ran the
tests ignoring non-related tasks (line 3).  In addition, when we run a
subject's test suite, we operate Maven in offline mode to limit the
network access, avoiding any unnecessary package update as all
required \emph{jars} are available locally (line 2). We also
considered the execution of all subjects enforcing sequential
execution to avoid having the real time cost masked by the use of any
parallel setting mentioned in Section~\ref{sec:modes} (line 4).  After
the test execution, we use a simple regular expression over the
builder output to extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip, go, offline, P},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn dependency:go-offline
mvn -o test -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true -P tests-seq
\end{lstlisting}
\caption{\label{fig:mvn-execution} Maven commands to test a subject:
    line 1 compiles all subject's source artifacts and make them
    available in a local repository (\ie, directory \emph{.m2} in the
    user's home directory); line 2 ensures all dependencies are
    resolved; line 3 runs the tests in offline mode ignoring javadoc
    generation; line 4 runs the tests using our \emph{tests-seq}
    profile to ensure sequential execution.}
\end{figure}

@@

Considering the groups \emph{medium} and \emph{long} (\Fix{X} subjects), we
investigated the relationship between the number of tests cases and the time
cost from subjects. \Fix{Explain what is correlation and how it is computed.}
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that the number
of tests cases are not related to the elapsed time.  \Fix{explain briefly what
dominates a test execution/types of tests}.Results indicate that
\Fix{...conclusion...}.}
